\subsection{Precision of Analyses}

Though the implemented analyses supported by the Analysis Engine provide information about the input programs, examples can still be crafted where the analysis provides less information than we ourselves would get from reading the input program. Examples of such "false positives" can be seen below. 

\newpar Analyses are not always precise, for example consider the following example:

\begin{minted}{c}
int x,a,b;
x = input();
if(x > 0){
	x = -1;
}
a = x - 1;
b = x - 2;
while (x>0){
	output a*b-x;
	x = x-1;
}
output a*b;
\end{minted}

\newpar A very busy expressions analysis would determine that \texttt{a*b} is a busy expression inside the \texttt{while} loop even though the loop is \emph{dead-code}, that is, code that is never executed. This seemingly limitation of the analysis actually suggest an \emph{analysis-transformation} pattern in which an user supplies a transformation function that would receive as arguments the least fix-point (e.g. \texttt{\_state}) and the CFG and it will return a transformed CFG. It is worth to mention that the order in which the analyses and their respective transformations are executed might impact the performance of the overall CFG transformation. 

\newpar To illustrate this point at an intuitive level, let us assume we have a very busy expression and sign analyses and a constrain solver with their respective transformations. If the busy expressions analysis is executed first, then the transformation would factor \texttt{a*b} out of the \texttt{while} loop and and add a temporal variable. Then the sign analysis would determine that \texttt{x} is less than or equal to $0$, in this case the transformation might be empty. Finally the constrain solver would determine that the condition of the \texttt{while} is impossible to satisfy and mark the loop as dead-code. On the other hand, if the sign analysis is executed first, then the constrain solver and finally the very busy expressions analysis the result would not have an extra (temporal) variable. However, both programs are semantically equivalent. 